\proglang{EpiCompare}: Working title

### 2020-05-02 jss/jss-article-rnw/chapters/ch3-time-free.Rnw
added 2 new articles and 1 citation to document.

$R_0$, the initial reproduction number, has been called the ``most important quantity in epdiemiology''. To see the importance of $R_0$, one need only read the newspaper \citep{FILL IN} or look at the length of the table of estimated $R_0$ quantities for COVID-19 \citep{FILL IN}. $R_O$ is also, maybe, the most famous \textit{time-free} numerical summary of an epidemic, and is most commonly associated with the Susceptible-Infectious-Recovered (SIR) data/models. The SIR framework, composed of data and statistical models where individuals pass from Susceptible to Infectious to Recovered states is a common, if not the most common, modeling framework in infectious disease epidemiology (seen in examples of recent published works in \cite{FILL IN}).

>>>>

$R_0$, the initial reproduction number, has been called the ``most important quantity in epdiemiology''. To see the importance of $R_0$, one need only read the newspaper \citep{Fisher2020} or look at the length of the table of estimated $R_0$ quantities for COVID-19 \citep{FILL IN}. $R_O$ is also, maybe, the most famous \textit{time-free} numerical summary of an epidemic, and is most commonly associated with the Susceptible-Infectious-Recovered (SIR) data/models. The SIR framework, composed of data and statistical models where individuals pass from Susceptible to Infectious to Recovered states is a common, if not the most common, modeling framework in infectious disease epidemiology (seen in examples of recent published works in \cite{FILL IN}).
